---
title: "ARIMA-GARCH"
author: "ADHIL VENGAT"
date: "`r Sys.Date()`"
output: html_document
---


## Installing packages
```{r, eval=FALSE,echo=TRUE, warning=FALSE, message=FALSE}
rm(list=ls())
install.packages("FinTS")
install.packages("rugarch")
install.packages("tseries")
install.packages("dynlm")
install.packages("vars")
install.packages("nlWaldTest")
install.packages("broom")
install.packages("car")
install.packages("sandwich")
install.packages("knitr")
install.packages("forecast")
install.packages("ggplot2")
install.packages("pdfetch")
install.packages("tsbox")
install.packages("stats")
install.packages("zoo")
install.packages("vrtest")
install.packages("dsEssex")
install.packages("quantmod")
install.packages("PerformanceAnalytics")
install.packages("MLmetrics")
```
## Loading packages
```{r, eval=FALSE,echo=TRUE, warning=FALSE, message=FALSE}
library(FinTS)                   #For Arch Test
library(rugarch)                 #For GARCH model
library(tseries)                 #For unit root test
library(dynlm)                   #For using lags in the model
library(vars)                    #For using var
library(nlWaldTest)              #For testing non linear wald test
library(lmtest)                  #For BP test
library(broom)                   #For table presentation
library(car)                     #For robust standard errors
library(sandwich)
library(knitr)
library(forecast)
library(ggplot2)
library(pdfetch)                 #For importing Financial Data
library(tsbox)
library(stats)
library(zoo)
library(vrtest)
library(dsEssex)
library(xts)
require(dsEssex)
library(quantmod)
library(PerformanceAnalytics)
library(MLmetrics)
```

## Setting Theme
```{r}
theme_set(theme_bw())
```


## Collecting Data
```{r}
data <- read.csv("/Users/adhilvengat/Downloads/^NSEI.csv", header=TRUE, stringsAsFactors=FALSE)
df <- pdfetch_YAHOO(c("^nsei"),fields = c("close"),from = as.Date("2010-01-01"),to = as.Date("2021-01-01"))
```

## Visualising the series

```{r}
chart_Series(df)
```
##Converting to time series object
```{r}
dfts<- ts(df, start = c(2010,4),frequency = 365)
#data.frame(dfts)
```

## Step 1 Normality Test and log transformation if needed
```{r}
shapiro.test(dfts)
# it rejects null hypo since p-value  < 2.2^e-16
```

##Visualise
```{r}
require(dsEssex)
plot.ts(dfts)
title("Time series plot of Nifty50")
plot(df)
hist(dfts,main="Histogram of Nifty50",freq=FALSE,col="grey")
plot.ts(diff(dfts),ylab = "Change in Nifty50")
title("First Difference of Nifty50")
```
## Daily Returns ( see vid for exp)
```{r}
return <- CalculateReturns(df)
return <- na.omit(return)
hist(return)
chart.Histogram(return,
                methods = c('add.density', 'add.normal'),
                colorset = c('blue', 'green', 'red'))
# Green curve is density and Blue curve is distribution curve.
chartSeries(return)
```

## Annualized volatility (showing how volatilty changed over years)
```{r}

chart.RollingPerformance(R = return["2010::2020"],
                         width = 252,
                         FUN = "sd.annualized",
                         scale = 252,
                         main = "Apple's yearly rolling volatility")
```
## Check for stationarity of varience and mean
```{r}
plot.ts(return)
title("Time series Plot of log of Nifty50")

Auto.VR(return)  # Variance is not constant
adf.test(return,k=3)
# As we can see the H1 is true, the return is stationary no need of differencing
```
## Determining PACF(AR,p) and ACF(MA,q)
```{r}
acf.return  <-acf(return,main = "ACF(MA) of Nifty50", lag.max=50)
pacf.return <-pacf(return,main = "PACF(AR) of Nifty50", lag.max=50)

# ARIMA(6,1,5) is observed from plot.

```
##Step 4 Estimating ARIMA model using auto-arima
```{r}
auto.arima(return)
# ARIMA(5,0,2) for returns aremstationary unlike closing price

arima502 <- auto.arima(return)
summary(arima502)
tsdiag(arima502)
checkresiduals(arima502)
autoplot(arima502)


#residuals being added

arimar <- arima502$residuals
ggtsdisplay(arimar, main="NIFTY 50 ARIMA residuals")
```
## Step 5: Estimate mean Equation r = beta + error
```{r}
gsp.mean <- dynlm(arimar ~ 1)
summary(gsp.mean)

```

## Step 6 Determination of ARCH effect
```{r}
ehatsq <- ts(resid(gsp.mean)^2)
gsp.archef <- dynlm(ehatsq ~ L(ehatsq))
summary(gsp.archef)

```
## Testing Arch effect
```{r}

gsp.archef1 <- ArchTest(arimar, lags=1, demean = TRUE)
gsp.archef1
```


# 1. sGARCH model with constant mean
```{r}

s <- ugarchspec(mean.model = list(armaOrder = c(5,2)),
                variance.model = list(model = "sGARCH"),
                distribution.model = 'norm')
m <- ugarchfit(data = return, spec = s)
m
plot(m,which ="all")
f <- ugarchforecast(fitORspec = m, n.ahead = 20)
plot(fitted(f))
plot(sigma(f))

```

## Application example - portfolio allocation
```{r}
model = m 
v <- sqrt(252) * sigma(model) # Annualised volatilty stored in v
w <- 0.1/v                    # " w " is gthe weight assignrd to risky assets....i.e 10% risk in here (0.1)
plot(merge(v, w), multi.panel = T)

# Basically we can understand how much we can expect to risky assets using the respective model
```

## 2. GARCH with sstd
```{r}

s <- ugarchspec(mean.model = list(armaOrder = c(5,2)),
                variance.model = list(model = "sGARCH"),
                distribution.model = 'sstd')
m <- ugarchfit(data = return, spec = s)
m
plot(m, which="all")
```


## 3. ARMA (5,2) GJR-GARCH(1,1)
```{r}

s <- ugarchspec(mean.model = list(armaOrder = c(5,2)),
                variance.model = list(model = "gjrGARCH"),
                distribution.model = 'sstd')
m <- ugarchfit(data = return, spec = s)
m
plot(m , which="all")
```



## 4. ARMA(5,2)- eGARCH
```{r}

s <- ugarchspec(mean.model = list(armaOrder = c(5,2)),
                variance.model = list(model = "eGARCH"),
                distribution.model = 'sstd')
m <- ugarchfit(data = return, spec = s)
m
plot(m , which="all")
```
## 5. ARMA(5,2)- ApARCH
```{r}

s <- ugarchspec(mean.model = list(armaOrder = c(2,2)),
                variance.model = list(model = "apARCH"),
                distribution.model = 'sstd')
m <- ugarchfit(data = return, spec = s)
m
plot(m , which="all")
```

## Simulating the stock price from model(returns )
## 4. ARMA(5,2)- eGARCH
```{r}

s <- ugarchspec(mean.model = list(armaOrder = c(4,2)),
                variance.model = list(model = "eGARCH"),
                distribution.model = 'sstd')
m <- ugarchfit(data = return, spec = s)
m
plot(m , which="all")
```


```{r}

#s <- ugarchspec(mean.model = list(armaOrder = c(5,2)),variance.model = list(model = "eGARCH"),distribution.model = 'sstd')

m <- ugarchfit(data = return, spec = s)
m
sfinal <- s
setfixed(sfinal) <- as.list(coef(m))
# Forecasting for 3 year 
#f2020 <- ugarchforecast(data = return["/2020-12"], fitORspec = sfinal, n.ahead = 30, n.roll = 2663, out.sample = 2663)
par(mfrow = c(1,1))
#plot(sigma(f2020))
sim <- ugarchpath(spec = sfinal,
                  m.sim = 2,
                  n.sim = 1*10,
                  rseed = 123,n.ahead = 10, n.roll = 2664, data = return, out.sample = 2664)
plot.zoo(fitted(sim))
plot.zoo(sigma(sim))
tail(df)
p <- 13981.75*apply(fitted(sim), 2, 'cumsum') + 13981.75
matplot(p, type = "l", lwd = 3)
```

## Forecasting for next 30 days
```{r}
n1_garch <- m
n1_garch_predict <- ugarchboot(n1_garch, n.ahead = 10,method = c("Partial","Full")[1])
n1_garch_predict

plot(n1_garch_predict,which = "all")
```





```{r}
actual <- pdfetch_YAHOO(c("^nsei"),fields = c("close"),from = as.Date("2021-01-01"),to = as.Date("2021-01-15"))
chart_Series(actual)

z1 <- actual
x <- c(1,2,3,4,5,6,7,8,9,10)
count <- 0
for (i in x){
  z1$`^nsei`[i]<-p[,2][i] 
  count=count+1
}
pred = z1

#MAE
MAE(pred, actual)


#MAPE
MAPE(pred, actual)

#MSE
MSE(pred, actual)

#RMSE
RMSE(pred, actual)

```




```{r}
t=1:10
z1= fact_check
x <- c(1,2,3,4,5,6,7,8,9,10)
count <- 0
for (i in x){
  z1$`^nsei`[i]<-p[,2][i] 
  count=count+1
}
z = z1
w= p[,2]
plot(actual, type="l", col="green", lwd=10,xlim = 16000, xlab="DAYS", ylab="CLOSING PRICE")
lines(z , col="red", lwd=1)
title("ACTUAL vs FORECAST")
legend("left",14500,legend=c("Actual","Forecast"),col=c("green","red"),lty=1)
#legend(2,1,c("actual","forecast"), lwd=c(5,2), col=c("green","red"))




```
```{r}
p[,2]
z1= fact_check
x <- c(1,2,3,4,5,6,7,8,9,10)
count <- 0
for (i in x){
  z1$`^nsei`[i]<-p[,2][i] 
  count=count+1
}

```



```{r}

MAPE(z, fact_check)


```







```{r}

```



```{r}

```



```{r}

```



```{r}

```



